\newpage
\subsection{Recommendations}        

To enhance the overall security of \clientNoSpace, \team recommends implementing the following measures: 

\begin{enumerate}
    \item \textbf{Immediate segmentation and authentication for safety-critical systems:} The ballast control and navigation (Bridge) systems must be treated as high-security system to prevent remote manipulations by an attacker from having physical consequences. \team recommends that the default guest account on the Ballast system be disabled immediately. Concurrently, the Bridge Command Center must be placed behind a login screen enforced with Strong Multi-Factor Authentication (MFA). Crucially, these systems should be network-segmented via VLANs so they are effectively isolated from the general corporate network, providing an additional layer of defense in depth against access from unauthorized networks. \team expects this to cost \$400-\$500 for the new router, cables, and other hardware to isolate these systems and take approximately 3-5 months.

    \item \textbf{Implement a web application firewall (WAF):} \teamP testing revealed a severe "Local File Inclusion" (LFI) vulnerability in the ship's API. By manipulating the file download functionality, \team successfully extracted master database credentials. This access granted full read/write privileges to the GPS Tracker database, allowing \team to modify live operational data and exfiltrate sensitive navigation logs. \teamP recommends that \client implements a web application firewall (WAF) to provide defense in depth against such vulnerabilities. \team expects this to cost \$0 (as free and open-source WAF solutions such as ModSecurity and Coraza exist) and take between 1-2 weeks, as the WAF needs to be tweaked with rules that will result in few false positives.
    
    \item \textbf{Enforce strong identity policies and harden Active Directory:}  
    \teamP found that the company-wide password policy only requires passwords of 5 or more characters long, which falls far behind industry current best practices and requirements of 14-character-long passwords. In addition, all Active Directory accounts should be audited to ensure that they follow the Principle of Least Privilege. \team expects this to cost \$0 and take between 2-3 months, as \client has an exceptionally large Active Directory domain of over 2500 users. 
\end{enumerate}